---
title: "JPL Spectroscopy"
author: "David Josephs, John Partee"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
    number_sections: true
    theme: united
    highlight: haddock
    df_print: paged
    keep_md: TRUE
    fig_width: 10
    fig_height: 10
    fig_retina: true
---

```{r setup, include = F}
knitr::opts_chunk$set(warning = F, message = F, dev = "svg", fig.align = "center")
knitr::opts_chunk$set(tidy = T)
knitr::opts_chunk$set(comment = '#>')
options(digits = 2)
```


# Installation

First, install the requirements:

```bash
pip install -r requirements.txt
```

This is included in the zip file, however they are listed here for transparency:

```bash
plotly
tqdm
numpy
matplotlib
scipy
astropy
requests-html
astroquery
beautifulsoup4
```

## Project Layout (for now)

Next, start working relative to the jplspec (for example if you were working on a project called `myproject.py`):

```bash
.
├── jplspec
│   ├── __init__.py
│   ├── molecules.py
│   ├── setcover.py
│   ├── spectraldata.py
│   └── utility.py
├── project.py
├── README.md
└── requirements.txt
```

Now we can start running the code!

# Loading the data:

First, we import the library:

```{python}
import jplspec as jpl


```

## The SpectralFile and SpectralData classes

Now we can reference the file with the `SpectralFile` class, and then `read` it into a `SpectralData` object:

```{python}
path ="Titan/Titan/Win0.clean1.contsub_Jy.rest.scom.c.txt"
myfile = jpl.SpectralFile(path)
print(myfile)

data = jpl.read(myfile)
print(data)
```

Note we can wrap this all in one step with:

```python
data = jpl.read(jpl.SpectralFile(path))
```

Please also note optional keyword arguments: `name, temperature, time, data, units`. These are not necessary, however they may be useful from an organizational perspective. All attributes of all objects in the `jplspec` library can be accessed via `object.attribute`

# Spike Identification and Database Querying

Now we can identify the spikes!

## Spike identification

Identified using a three sigma threshold. This can be modified by writing a custom function that returns indices of true cases using `np.where`, and using the `spike_method` argument

```{python}
spikes = jpl.identify_spikes(data)
jpl.plot_spikes(spikes)
print(spikes)
```

### Adjusting the spike identification method

To adjust the spike identification method, we write a function which returns a boolean value. We have 4 attributes to play with, `intensity`, `frequency`, `std`, and `mean`. These are all optinally used, so we can write spike identification methods with whatever we want. As an example, if we are looking for two sigma events, we could write:
```python
def two_sigma_spike(x):
  return x.intensity > (x.mean + 2 * x.std)
```

## Finding associated molecules from the spikes

Next, we query the spectroscopy datasets for our spikes:

```{python}
molecules = jpl.get_molecules_from_spikes(spikes, save_path="win0.dmp")
```

Note this will only take a long time once if we use the save_path argument. This saves the molecule information in a standard python dictionary.

# Set covering

Finally, we can score all the molecules and generate the sets!

```{python}
import pprint
result = jpl.SetCovering(spikes, molecules)
scored_molecules = result.likeliest_molecules()
scored_sets = result.likeliest_sets()
pprint.pprint(scored_molecules)
pprint.pprint(scored_sets[0])
fig = result.visualize() # lines is a height scaling parameter
```

We can visualize this with `fig.show()`, just like matplotlib:
```{python, echo=F}
fig.write_html("ok.html")
```

```{r, echo=F}
htmltools::includeHTML("ok.html")
```

